\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-12 ext-ind-type-compilation-example.tex
Tidy up the example, with one new ctx.

\begin{lstlisting}
(* **Type Checking of Inductive Type** *) [@\tanc{Cmp-Result0-start}@]
Module Type STLC_Ctx1. 
(* The Context including Inductive Type *)
  Parameter (tm : Set).
  Parameter (tm_var : id → tm).
  Parameter (tm_abs : id → tm → tm).
  (* [@\dadada@] and all the fields for inductive type [@\dadada@] *)
End STLC_Ctx1.
Module Type tm_prec_64 (self: tm_6). (* Type for partial recursor *)
Parameter
  (tm_prec :
  forall i : self.tm, forall P : self.tm -> Type,
  (forall n, option (P (self.tm_var n))) ->
  [@\dadada@], option (P i)).
End tm_prec_64.
Module Type STLC_Ctx2. (* The Context including partial recursor *) 
  Include STLC_Ctx1.
  Include tm_prec_64.
End STLC_Ctx2.
(* [@\dadada@] etc, for every context, (everytime a new field is added) we will construct a new context as module type *)
(* Collect eliminator TYPE for later type-check *)
Module tm_rec_type (self: STLC_Ctx1).
  Definition __recursor_type_tm_rec :=
    forall P : self.tm -> Set,
    (forall n : id, P (self.tm_var n)) ->
    (forall (n : id) (i : self.tm),
    P i -> P (self.tm_abs n i)) ->
    [@\dadada@] -> forall i : self.tm, P i.
End tm_rec_type.  
(* **Type checking of Recursion** *)
(* Typecheck each handler, here STLC.subst.tm_var *)
(* Also an example of fields in nested family, thus with two contexts *) 
Module tm_var_handle (self__STLC: STLC_Ctx1)
    (self__subst_internal: EmptySig_84).
  Definition tm_var :
    forall (s : ident) (x : ident) 
    (t : self__STLC.tm), self__STLC.tm :=
    fun s x t => if eqb x s
       then t else self__STLC.tm_var s.
End tm_var_handle. (* [@\dadada@] and more *)
(* Assembling tycked handlers in STLC.subst during compilation *)
Module subst_internal_410 (STLC: STLC_Ctx1). 
 Module subst_internal.
 Include tm_var_handle STLC. Include tm_abs_handle STLC.
 Include tm_app_handle STLC. Include tm_unit_handle STLC.
 End subst_internal.
End subst_internal_410.
(* Intermediate Module solely for exhausitivity checking *) 
Module do_tc (self: STLC_Ctx[@\dadada@]).
  Include tm_rec_type self.
  Parameter (recursor_for_type_checking 
    : __recursor_type_tm_rec).
  Definition term_for_type_checking :=
    recursor_for_type_checking 
      (fun _  ⇒ id → self.tm → self.tm)
      subst_internal_410.tm_var [@\dadada@] .
End do_tc.
[@\tanc{Cmp-Result0-end}@]
\end{lstlisting}

\makeline[0pt]{Cmp-Result0-start}{Cmp-Result0-end}[codecomment-color!50]

@@

\begin{lstlisting}
[@\tanc{Cmp-Result-start}@]
(* Exposing Computational Axiom into Ctx *)
Module Type substtm_139 (self: STLC_Ctx[@\dadada@]).
Parameter
  (subst_on_tm_unit :
	 (self.subst (self.tm_unit)) = 
      self.subst_internal.tm_unit).
(* [@\dadada@] subst equality on other constructors *)
End substtm_139.

(* Compilation, only when closing a top-level family *)
(* Ctx that expose concrete inductive type *)
Module Type ctx_subst_113.
Inductive __internal_tm : Set := [@\dadada@] 
Include subst_internal_410. (* [@\dadada@] and more inclusion *)
End ctx_subst_113.
(* Compilation of recursor, 
  require concrete inductive type in the ctx *)
Module subst_128 (self: ctx_subst_113).
Include __motive_of_subst_107 self.
Definition subst :=
  self.__internal_tm_rec __motiveTsubst
	self.subst_internal.tm_var [@\dadada@] .
End subst_128.
(* Compilation of Partial Recursor *)
Module tm_prec_72 (self: STLC_Ctx1).
Definition tm_prec :
  forall i : self.tm, forall P : self.tm -> Type,
  (forall n, option (P (self.tm_var n))) ->
  [@\dadada@], option (P i) :=
End tm_prec_72. 
(* Assembling/Compiling the whole STLC *)
Module STLC.
Include tm_5. Include tm_prec_72. Include tm_prectm_81.
Include subst_internal_410. Include subst_128.
End v_129.
(* Assembling STLC_bool.subst_internal via reusing 
    most of the former compilation results *)
Module subst_internal_248 (STLC_bool: STLC_Ctx1).
Include tm_true_197 STLC_bool. Include [@\dadada@]
(* The Reused Compilation result *)
Include tm_var_handle STLC_bool. Include [@\dadada@]
End v_248. 
(* Regenerated FRecursion result *)
Module subst_242 (self__STLC_bool: [@\dadada@]).
Include __motive_of_subst_107 self__STLC_bool.
Definition subst :=
  self__STLC_bool.__internal_tm_rec __motiveTsubst
	self__STLC_bool.subst_internal.tm_var [@\dadada@]
    self__STLC_bool.subst_internal.tm_true [@\dadada@] .
End subst_242. [@\tanc{Cmp-Result-end}@]
\end{lstlisting}

@@

\caption{Exemplar Compilation about Inductive Type}\label{fig:plugin-example2}
\end{figure}

>>>>

\begin{lstlisting}
(* Type Checking of Inductive Type *) [@\tanc{Tyck-IndTy-start}@]
Module Type STLC_Ctx1. 
(* The Context including Inductive Type *)
  Parameter (tm : Set).
  Parameter (tm_var : id → tm).
  Parameter (tm_abs : id → tm → tm).
  (* [@\dadada@] and all the fields for inductive type [@\dadada@] *)
End STLC_Ctx1.
Module Type tm_prec_64 (self: tm_6). 
Parameter (* Type for partial recursor *)
(tm_prec : ∀ t, ∀ P : self.tm -> Type,
  (∀ n, option (P (self.tm_var n))) -> 
  [@\dadada@], option (P t)).
End tm_prec_64.
Module Type STLC_Ctx2.  
  Include STLC_Ctx1.
  Include tm_prec_64. (* New Ctx include prec *)
End STLC_Ctx2.
(* [@\dadada@] etc, everytime a new field is added, a new 
module type is created as the ctx with the new field *)
(* Collect eliminator TYPE for later type-check *)
Module tm_rec_type (self: STLC_Ctx1).
  Definition _TYPE_tm_rec :=
    ∀ P : self.tm -> Set,
    ( ∀ n, P (self.tm_var n)) ->
    ( ∀ n i, P i -> P (self.tm_abs n i)) ->
    [@\dadada@] -> ∀ i : self.tm, P i.
End tm_rec_type.  [@\tanc{Tyck-IndTy-end}@]
\end{lstlisting}

\makeline[0pt]{Tyck-IndTy-start}{Tyck-IndTy-end}[codecomment-color!50]

\definecolor{codecomment-color}{HTML}{0DA30F}

\begin{lstlisting}
(* Type checking of Recursion *) [@\tanc{Tyck-RecTy-start}@]
(* Typecheck each handler, here STLC.subst.tm_var *)
(* Also an example of fields in nested family [@\dadada@]*) 
Module tm_var_handle (STLC: STLC_Ctx1)
    (self: EmptySig). (* [@\dadada@] thus with two contexts *) 
  Definition tm_var s x t := 
    if eqb x s then t else STLC.tm_var s.
End tm_var_handle. (* [@\dadada@] other handlers are alike *)
(* Assembling tycked handlers in STLC.subst *)
Module subst_internal_410 (M: STLC_Ctx1). 
 Module subst_internal.
 Include tm_var_handle M. Include tm_abs_handle M.
 Include tm_app_handle M. Include tm_unit_handle M.
 End subst_internal.
End subst_internal_410.
(* Intermediate Module solely for exhausitivity checking *) 
Module do_tc (self: STLC_Ctx[@\dadada@]).
  Include tm_rec_type self. 
  Include subst_internal_410 self.
  Parameter (for_tyck : _TYPE_tm_rec).
  Definition term_for_type_checking :=
    for_tyck  ( λ _  ⇒ (id → self.tm → self.tm))
      subst_internal.tm_var [@\dadada@] .
End do_tc.[@\tanc{Tyck-RecTy-end}@]
\end{lstlisting}

\makeline[0pt]{Tyck-RecTy-start}{Tyck-RecTy-end}[codecomment-color!50]

@@

\begin{lstlisting}
(* Exposing Computational Axiom into Ctx *) [@\tanc{Tyck-Recty-cont-start}@]
Module Type substtm_139 (self: STLC_Ctx[@\dadada@]).
Parameter
  (subst_on_tm_unit :
	 (self.subst (self.tm_unit)) = 
      self.subst_internal.tm_unit).
(* [@\dadada@] subst equality on other constructors *)
End substtm_139. [@\tanc{Tyck-Recty-cont-end}@]
\end{lstlisting}

\makeline[.5\textwidth+9pt]{Tyck-Recty-cont-start}{Tyck-Recty-cont-end}[codecomment-color!50]

\definecolor{codecomment-color}{HTML}{5D030F}

\begin{lstlisting}
(* Compilation, only when closing a top-level family *) [@\tanc{Cmp-Result-start}@]
(* Ctx that expose concrete inductive type *)
Module Type STLC_CCtx1.
Inductive __internal_tm : Set := [@\dadada@] 
Include subst_internal_410. (* [@\dadada@] and more inclusion *)
End STLC_CCtx.
(* The compilation of recursor and[@\dadada@] *)
Module subst_128 (self: STLC_CCtx1).
Include __motive_of_subst_107 self.
Definition subst :=
  self.__internal_tm_rec __motiveTsubst
	self.subst_internal.tm_var [@\dadada@] .
End subst_128.
(* [@\dadada@] the compilation of partial recursor, 
both require concrete inductive type in the ctx *)
Module tm_prec_72 (self: STLC_CCtx1).
Definition tm_prec :
  ∀ t, ∀ P : self.tm -> Type,
  (∀ n, option (P (self.tm_var n))) ->
  [@\dadada@], option (P t) := [@\dadada@]
End tm_prec_72. 
Module STLC. (* Assembling/Compiling the whole STLC *)
Include tm_5. Include tm_prec_72. 
Include tm_prectm_81. (* Justification for comp axiom *)
Include subst_internal_410. Include subst_128.
End v_129.
(* Assembling STLC_bool.subst_internal via reusing 
    most of the former compilation results *)
Module subst_internal_248 (STLC_bool: STLC_Ctx1).
Include tm_true_197 STLC_bool. Include [@\dadada@]
(* The Reused Compilation result *)
Include tm_var_handle STLC_bool. Include [@\dadada@]
End v_248. 
(* Regenerated FRecursion Compilation *)
Module subst_242 (self: [@\dadada@]).
Include __motive_of_subst_107 self.
Definition subst :=
  self.__internal_tm_rec __motiveTsubst
	self.subst_internal.tm_var [@\dadada@]
    self.subst_internal.tm_true [@\dadada@] .
End subst_242. [@\tanc{Cmp-Result-end}@]
\end{lstlisting}

@@

\caption{Exemplar Compilation about Inductive Type, for STLC example}\label{fig:plugin-example2}
\end{figure}
